Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-09-01 Docs/Paper/LaTex/template.tex
fix references

%1
\bibitem{Arato2003}
Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D., ``{Hardware/software partitioning in embedded system design. In: Proceedings of the International Symposium of Intelligent Signal Processing},'' pp. 192-202 (2003)

@@

%3
\bibitem{Baier2008}
Baier, C., Katoen, J-P. ``{Principles of Model Checking. The MIT Press, London (2008)}''

%4
\bibitem{Clarke2009}
Clarke, E., Emerson, E., Sifakis, J. ``{Model checking: algorithmic verification and debugging. In: Communications of the Association Computing Machinery (ACM), vol. 52, i. 11},'' pp. 74-84 (2009)

%5
\bibitem{Trindade2015}
Trindade, A., Cordeiro. L. ``{Applying SMT-based verification to hardware/software partitioning in embedded systems. In: Design Automation for Embedded Systems. Springer, New York (2015)}''

%6
\bibitem{Trindade2014}
Trindade, A., Cordeiro, L. ``{Aplicando Verificação de Modelos para o Particionamento de Hardware/Software. In: Brazilian Symposium on Computing Systems Engineering (SBESC), 2014, Manaus – AM, Brazil. Anais SBESC},'' pp. 1-6 (2014).

%7
\bibitem{Wu2014}
Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N. ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP. In: International Conference on Software Engineering and Service Science (ICSESS)},'' pp. 921,924, IEEE (2014)

%8
\bibitem{Tang2009}
Tang, T., Lin, Y., Ren, X. ``{Mapping OpenMP concepts to the stream programming model. In: Int. Conference on Computer Science Education (ICCSE)},'' pp. 1900-1905, IEEE (2010)

%9
\bibitem{Rao2009}
Rao, S. ``{Engineering Optimization: Theory and Practice. 4th edition. John Wiley \& Sons, Hoboken (2009)}''

%10
\bibitem{Biere2009}
Biere, A. ``{Bounded model checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.) Handbook of Satisfiability, IOS Press, pp. 457–481, Amsterdam (2009)}''

%11
\bibitem{Clarke2004}
Clarke, E., Kroening, D., Lerda, F. ``{A Tool for Checking ANSI-C Programs. In: Proceedings of the Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 2988}'', pp. 168-176 (2004)

%12
\bibitem{Armando2009}
Armando, A., Mantovani, J., Platania, L. ``{Bounded model checking of software using SMT solvers instead of SAT solvers. In: International Journal on Software Tools for Technology Transfer, Vol. 11, n. 1},'' pp. 69-83 (2009)

%13
\bibitem{Ganai2006}
Ganai, M., Gupta, A. ``{Accelerating high-level bounded model checking. In: Proceedings of the IEEE/ACM International Conference on Computer-Aided Design},'' pp. 794–801 (2006)

%14
\bibitem{Cordeiro2012}
Cordeiro, L., Fischer, B., Marques-Silva, J. ``{SMT-based bounded model checking for embedded ANSI-C software. In: IEEE Transactions on Software Engineering, vol. 38, ed. 4},'' pp. 957-974 (2012)

%15
\bibitem{Cordeiro2011}
Cordeiro, L., Fischer, B. ``{Verifying multi-threaded software using SMT-based context-bounded model checking. In: Proceedings of the 33rd International Conference on Software Engineering},'' pp. 331-340 (2011)

%16
\bibitem{Ramalho2013}
Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L. ``{SMT-Based Bounded Model Checking of C++ Programs. In: International Conference and Workshops on the Engineering of Computer-Based Systems},'' pp. 147-156, IEEE (2013)

%17
\bibitem{Teich2012}
Teich, J. ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future. In: Proceedings of the IEEE, vol. 100},'' pp. 1411-1430 (2012)

%18
\bibitem{TheMathWorks2013}
The MathWorks, Inc ``{MATLAB (version R2013a). Natick, MA (2013)}''

%19
\bibitem{Tranquillo2011}
Tranquillo, J. ``{Matlab for Engineering and the Life Sciences. Synthesis Lectures on Engineering. Morgan \& Claypool (2011)}''

%20
\bibitem{Hong2010}
Hong, L., Cai, J. ``{The application guide of mixed programming between MATLAB and other programming languages. In: Proceedings of the 2nd International Conference on Computer and Automation Engineering (ICCAE)},'' pp. 185-189 (2010)

%21
\bibitem{Guthaus2001}
Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R. ``{MiBench: a free, commercially representative embedded benchmark suite. In: Proceedings of the IEEE 4th annual workshop on workload characterization},'' pp. 3-14 (2001)

%22
\bibitem{Arato2005}
Arat\'o, P., Mann, Z.A., Orb\'an, A. ``{Algorithmic aspects of hardware/software partitioning. In: Association Computing Machinery Transactions on Design Automation of Electronic Systems, vol. 1},'' pp. 136–156 (2005)

%23
\bibitem{Dagum1998}
Dagum, L., Menon, R. ``{OpenMP: an industry-standard API for shared-memory programming. In: Computational Science \& Engineering, vol. 5, issue 1},'' pp. 46-55, IEEE (1998)

%24
\bibitem{DeMoura2008}
De Moura, L., Bjorner, N. ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 4963},'' pp. 337–340, Springer (2008)

%25
\bibitem{Brummayer2009}
Brummayer, R., Biere, A. ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 5505},'' pp. 174–177, Springer (2009)

%26
\bibitem{Barrett2011}
Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. ``{CVC4. In: Computer-Aided Verification (CAV), LNCS 6806},'' pp. 171-177, Springer (2011)

%27
\bibitem{Bozzano2005}
Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R. ``{MathSAT: Tight integration of SAT and mathematical decision procedures. In: Journal of Automated Reasoning, Springer (2005)}''

%28
\bibitem{Dutertre2014}
Dutertre, B. ``{Yices 2.2. In: Computer-Aided Verification (CAV), LNCS 8559},'' pp. 737–744, Springer (2014)

%29
\bibitem{Holzmann2011}
Holzmann, G.J., Joshi, R., Groce, A. ``{Swarm Verification Techniques. In: IEEE Transactions on Software Engineering, vol. 37, issue 6},'' pp. 845, 857, IEEE (2011)

%30
\bibitem{Holzmann2012}
Holzmann, G. ``{Parallelizing the spin model checker. In: Proceedings of the 19th International Conference on Model Checking Software (SPIN 2012), LNCS 7385},'' pp. 155-171, Springer (2012)

%31
\bibitem{Wintersteiger2009}
Wintersteiger, C., Hamadi, Y., De Moura, L. ``{A Concurrent Portfolio Approach to SMT Solving. In: International Conference on Computer-Aided Verification (CAV), LNCS 5643},'' pp. 715-720, Springer (2009)

%32
\bibitem{Bjorner2015}
Bjorner, N., Phan, A-D., Fleckenstein, L. ``{vZ - An Optimizing SMT Solver. In: International Conference on Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 9035},'' pp. 194-199, Springer (2015)

%33
\bibitem{Qawasmeh2014}
Qawasmeh, A., Malik, A., Chapman, B. ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization. In: Parallel \& Distributed processing symposium work-shop (IPDPSW), 2014 IEEE International},'' pp. 1049-1058, IEEE (2014)

%34
\bibitem{Bjorner2014}
Nikolaj Bjorner and Anh-Dung Phan ``{vZ - Maximal Satisfaction with Z3. SCSS 2014. 6th International Symposium on Symbolic Computation in Software Science.}''

@@

%39
\bibitem{Federica2008}
Federica, P., Rodolfo, F., Yuqing , S., Elisa, B., {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, Service-Oriented Computing – ICSOC 2008 Lecture Notes in Computer Science, 2008, Volume 5364/2008, 116-131

%40
\bibitem{Barth1995}Barth, P., Davis-Putnam, A., {``Enumeration Algorithm for Linear
Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science, 1995.

>>>>

%1
\bibitem{Arato2003}
Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D. (2003), ``{Hardware/software partitioning in embedded system design. In: Proceedings of the International Symposium of Intelligent Signal Processing},'' pp. 192-202.

@@

%3
\bibitem{Baier2008}
Baier, C., Katoen, J-P (2008), ``{Principles of Model Checking. The MIT Press, London}''.

%4
\bibitem{Clarke2009}
Clarke, E., Emerson, E., Sifakis, J. (2009), ``{Model checking: algorithmic verification and debugging. In: Communications of the Association Computing Machinery (ACM), vol. 52, i. 11},'' pp. 74-84.

%5
\bibitem{Trindade2015}
Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems. In: Design Automation for Embedded Systems. Springer, New York.}''

%6
\bibitem{Trindade2014}
Trindade, A., Cordeiro, L. (2014), ``{Aplicando Verificação de Modelos para o Particionamento de Hardware/Software. In: Brazilian Symposium on Computing Systems Engineering (SBESC)},'' pp. 1-6.

%7
\bibitem{Wu2014}
Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N. (2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP. In: International Conference on Software Engineering and Service Science (ICSESS)},'' pp. 921,924.

%8
\bibitem{Tang2009}
Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Int. Conference on Computer Science Education (ICCSE)},'' pp. 1900-1905.

%9
\bibitem{Rao2009}
Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition. John Wiley \& Sons, Hoboken}''.

%10
\bibitem{Biere2009}
Biere, A. (2009), ``{Bounded model checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.) Handbook of Satisfiability, IOS Press, pp. 457–481.}''

%11
\bibitem{Clarke2004}
Clarke, E., Kroening, D., Lerda, F. (2004), ``{A Tool for Checking ANSI-C Programs. In: Proceedings of the Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 2988}'', pp. 168-176.

%12
\bibitem{Armando2009}
Armando, A., Mantovani, J., Platania, L. (2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers. In: International Journal on Software Tools for Technology Transfer, Vol. 11, n. 1},'' pp. 69-83.

%13
\bibitem{Ganai2006}
Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking. In: Proceedings of the IEEE/ACM International Conference on Computer-Aided Design},'' pp. 794–801.

%14
\bibitem{Cordeiro2012}
Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based bounded model checking for embedded ANSI-C software. In: IEEE Transactions on Software Engineering, vol. 38, ed. 4},'' pp. 957-974.

%15
\bibitem{Cordeiro2011}
Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking. In: Proceedings of the 33rd International Conference on Software Engineering},'' pp. 331-340.

%16
\bibitem{Ramalho2013}
Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L. (2013), ``{SMT-Based Bounded Model Checking of C++ Programs. In: International Conference and Workshops on the Engineering of Computer-Based Systems},'' pp. 147-156.

%17
\bibitem{Teich2012}
Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future. In: Proceedings of the IEEE, vol. 100},'' pp. 1411-1430.

%18
\bibitem{TheMathWorks2013}
The MathWorks, Inc. (2013), ``{MATLAB (version R2013a). Natick, MA}''.

%19
\bibitem{Tranquillo2011}
Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences. Synthesis Lectures on Engineering. Morgan \& Claypool}''.

%20
\bibitem{Hong2010}
Hong, L., Cai, J. (2010), ``{The application guide of mixed programming between MATLAB and other programming languages. In: Proceedings of the 2nd International Conference on Computer and Automation Engineering (ICCAE)},'' pp. 185-189.

%21
\bibitem{Guthaus2001}
Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R. (2001), ``{MiBench: a free, commercially representative embedded benchmark suite. In: Proceedings of the IEEE 4th annual workshop on workload characterization},'' pp. 3-14.

%22
\bibitem{Arato2005}
Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning. In: Association Computing Machinery Transactions on Design Automation of Electronic Systems, vol. 1},'' pp. 136–156.

%23
\bibitem{Dagum1998}
Dagum, L., Menon, R. (1998), ``{OpenMP: an industry-standard API for shared-memory programming. In: Computational Science \& Engineering, vol. 5, issue 1},'' pp. 46-55.

%24
\bibitem{DeMoura2008}
De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 4963},'' pp. 337–340.

%25
\bibitem{Brummayer2009}
Brummayer, R., Biere, A. (2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 5505},'' pp. 174–177.

%26
\bibitem{Barrett2011}
Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4. In: Computer-Aided Verification (CAV), LNCS 6806},'' pp. 171-177.

%27
\bibitem{Bozzano2005}
Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R. (2005), ``{MathSAT: Tight integration of SAT and mathematical decision procedures. In: Journal of Automated Reasoning.}''

%28
\bibitem{Dutertre2014}
Dutertre, B. (2014), ``{Yices 2.2. In: Computer-Aided Verification (CAV), LNCS 8559},'' pp. 737–744.

%29
\bibitem{Holzmann2011}
Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques. In: IEEE Transactions on Software Engineering, vol. 37, issue 6},'' pp. 845, 857.

%30
\bibitem{Holzmann2012}
Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proceedings of the 19th International Conference on Model Checking Software (SPIN 2012), LNCS 7385},'' pp. 155-171.

%31
\bibitem{Wintersteiger2009}
Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving. In: International Conference on Computer-Aided Verification (CAV), LNCS 5643},'' pp. 715-720.

%32
\bibitem{Bjorner2015}
Bjorner, N., Phan, A-D., Fleckenstein, L. (2015), ``{vZ - An Optimizing SMT Solver. In: International Conference on Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 9035},'' pp. 194-199.

%33
\bibitem{Qawasmeh2014}
Qawasmeh, A., Malik, A., Chapman, B. (2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization. In: Parallel \& Distributed processing symposium work-shop (IPDPSW), 2014 IEEE International},'' pp. 1049-1058.

%34
\bibitem{Bjorner2014}
Bjorner, N. and Phan, A. D. (2014), ``{vZ - Maximal Satisfaction with Z3. 6th International Symposium on Symbolic Computation in Software Science (SCSS).}''

@@

%39
\bibitem{Federica2008}
Federica, P., Rodolfo, F., Yuqing , S., Elisa, B. (2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, Service-Oriented Computing – ICSOC 2008 Lecture Notes in Computer Science, 2008, Volume 5364, 116-131

%40
\bibitem{Barth1995}
Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.
